---
title: Homework 3
author: Duke Dinosaurs Team 4
date: "October 24, 2015"
output: html_document
---
1. Cleaning Data 
Since we have such a large dataset, we begin by learning some things about our data. Then, we can begin cleaning the data, so we have accurate data to work with. 
Let's take a look at what kind of information our data tells us.     
`colnames(nyc)`
We'll get back the folowing results       
 [1] "Unique.Key"                     "Created.Date"                  
 [3] "Closed.Date"                    "Agency"                        
 [5] "Agency.Name"                    "Complaint.Type"                
 [7] "Descriptor"                     "Location.Type"                 
 [9] "Incident.Zip"                   "Incident.Address"              
[11] "Street.Name"                    "Cross.Street.1"                
[13] "Cross.Street.2"                 "Intersection.Street.1"         
[15] "Intersection.Street.2"          "Address.Type"                  
[17] "City"                           "Landmark"                      
[19] "Facility.Type"                  "Status"                        
[21] "Due.Date"                       "Resolution.Description"        
[23] "Resolution.Action.Updated.Date" "Community.Board"               
[25] "Borough"                        "Park.Facility.Name"            
[27] "Park.Borough"                   "School.Name"                   
[29] "School.Number"                  "School.Region"                 
[31] "School.Code"                    "School.Phone.Number"           
[33] "School.Address"                 "School.City"                   
[35] "School.State"                   "School.Zip"                    
[37] "School.Not.Found"               "School.or.Citywide.Complaint"  
[39] "Vehicle.Type"                   "Taxi.Company.Borough"          
[41] "Taxi.Pick.Up.Location"          "Bridge.Highway.Name"           
[43] "Bridge.Highway.Direction"       "Road.Ramp"                     
[45] "Bridge.Highway.Segment"         "Garage.Lot.Name"               
[47] "Ferry.Direction"                "Ferry.Terminal.Name"   
Since some of these aren't important, we'll subset our `nyc` data to just the following fourteen variables.
```{r}
nyc.important <- nyc[,c("Unique.Key", "Complaint.Type", "Descriptor", "Incident.Zip", 
"Incident.Address", "Street.Name", "Cross.Street.1", "Cross.Street.2", "Intersection.Street
.1", "Intersection.Street.2", "Address.Type", "City", "Resolution.Description", "Borough")]
```

We can begin by subsetting out the two Street Intersection Columns.    
`test1 <- nyc.important$Intersection.Street.1 != ""`    
`test2 <- nyc.important$Intersection.Street.2 != ""`    
`> length(which(test1))`     
`[1] 1817002`     
`> length(which(test2))`     
`[1] 1816062`     
So we can see that there exists cases where Intersection.Street.1 has data but Intersetion.Street.2 does not. This may also be true vice-versa. 
```{r}
nyc.important.2 <- nyc.important[which(nyc.important$Intersection.Street.1 != ""),]
nyc.important.2 <- nyc.important.2[which(nyc.important.2$Intersection.Street.2 != ""),]
```
nyc.important.2 should only have the rows where Intersection.Street.1 and Intersection.Street.2 has data. 
```{r}
nyc.important.3 <- nyc.important.2[which(nyc.important.2$Cross.Street.1 != ""),]
```
Take out all data points where the Cross Street Columns and the Intersection Street Columns are empty. There is no location data for these calls and are useless to us for our purpose.  
```{r}
nyc3 <- filter(nyc.important, Cross.Street.1 != "" & Cross.Street.2 != "" & Intersection.Street.1 != "" & Intersection.Street.2 != "" )
```


